Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-24 Arxiv/main.tex
update
fix typo

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| $ can have $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible values, where $\sum{a_i} = \sum{b_i} = k$.
 \end{thm}

@@

 Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
 $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
 $|a_i|$ denotes the number of values in $\valpha$ having the value$a_i$ and $|b_i|$ the same in $\vbeta$.
 Then, by combination and permutation, there are $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible combination that satisfy the condition in Theorem \ref{thm_hellinegr_equality_dirichlet}.
 \end{proof}

>>>>

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| $ can have $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible values, where $\sum{|a_i|} = \sum{|b_i|} = k$.
 \end{thm}

@@

 Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
 $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
 $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
 Then, by combination and permutation rules, there are $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible combination that satisfy the condition in Theorem \ref{thm_hellinegr_equality_dirichlet}.
 \end{proof}
